Insert the article title here

### 2018-08-10 writeup/manuscript.tex
Changing figure size and reordering results section

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy in each of the three paradigms. We now turn our attention to which an individual's performance in one of the tasks tells us about how well they will do in the other two. As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors). Are individuals who are fast on one visual search task fast on another? In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

@@

The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms. While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of $r \in [0.65. 0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2018}. [AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]

>>>>

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy in each of the three paradigms. Furthermore, the split-half paradigm has a test-retest reliability of $r \in [0.65. 0.86]$, similar to that of the ACVS task ($r \in [0.72, 0.9]$), suggesting that the strategies different individuals chose to use in each of these tasks are somewhat stable. Given this, we now investigate the extent to which an individual's performance in one of the tasks tells us about how well they will do in the other two.

The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms. While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of  in the split-half paradigm and  for the adaptive choice paradigm\cite{irons-leber2018}. [AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]

@@

 As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors). Are individuals who are fast on one visual search task fast on another? In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@
